Automated iterative forecasting for the Portal Project

### 2018-01-22 manuscript/portal_iterative_forecasting_ms.Rmd

## Continuous Analysis Framewor

A core component of iterative near-term forecasting is the regular rerunning of forecasting pipeline. This can be conducted manually - with a human making sure all code is run and all tables and files are updated - or automatically by having the computer conduct those tasks. We chose to have the computer run our pipeline and employed "continuous analysis" [*sensu* @beaulieu2017] to drive the automation of both the full pipeline and a number of its individual components. Continuous analysis uses a set of tools originally designed for software development called "continuous integration" (CI). CI combines computing environments for running code with monitoring systems to identify changes in data or code. Essentially, CI is a computer helper whose job is to watch the pipeline and, when it sees a change in the code or data, it runs all the tasks needed to ensure that the forecasting pipeline runs from beginning to end. This is useful for iterative near-term forecasting because it does not rely on humans to remember to create forecasts when new models or data are added. These tools are common in the area of software development where they are used to automate software testing and integrate work by multiple software developers working on the same software. However, these tools can be used for any computational task that needs to be regularly repeated or run after changes to code or data [@beaulieu2017]. Because of the widespread use of CI in software development, several CI services already exist. Our forecasting pipeline currently runs on a publicly available continuous integration service (Travis CI; https://travis-ci.org/) that is free for open source projects (up to a limited amount of computing time); alternative services that can be used to run code on local or cloud-based computational infrastructure are available, such as Drone (http://try.drone.io/) [@beaulieu2017]. As detailed below, we use CI to quality check data, test code using "unit tests" [@wilson2014], build models, make forecasts, and publicly present and archive the results (Figure 2).

>>>>

## Continuous Analysis Framework

A core component of iterative near-term forecasting is the regular rerunning of forecasting pipeline. This can be conducted manually---with a human making sure all code is run and all tables and files are updated---or automatically by having the computer conduct those tasks. We chose to have the computer run our pipeline and employed "continuous analysis" [*sensu* @beaulieu2017] to drive the automation of both the full pipeline and a number of its individual components. Continuous analysis uses a set of tools originally designed for software development called "continuous integration" (CI). CI combines computing environments for running code with monitoring systems to identify changes in data or code. Essentially, CI is a computer helper whose job is to watch the pipeline and, when it sees a change in the code or data, it runs all the tasks needed to ensure that the forecasting pipeline runs from beginning to end. This is useful for iterative near-term forecasting because it does not rely on humans to remember to create forecasts when new models or data are added. These tools are common in the area of software development where they are used to automate software testing and integrate work by multiple software developers working on the same software. However, these tools can be used for any computational task that needs to be regularly repeated or run after changes to code or data [@beaulieu2017]. Because of the widespread use of CI in software development, several CI services already exist. Our forecasting pipeline currently runs on a publicly available continuous integration service (Travis CI; https://travis-ci.org/) that is free for open source projects (up to a limited amount of computing time); alternative services that can be used to run code on local or cloud-based computational infrastructure are available, such as Drone (http://try.drone.io/) [@beaulieu2017]. As detailed below, we use CI to quality check data, test code using "unit tests" [@wilson2014], build models, make forecasts, and publicly present and archive the results (Figure 2).
